SpecHunter: Interactively Inferring Taint Specifications Using Bayes Net

### 2021-04-04 My-Papers/SpecHunter/overview.tex
checkpoint

% TODO 아 이거 실제로 돌려봐서 확인해야 할 거 같은뎅.. 실제로 이렇게 나오나...?

@@

@@

% 여기서는 표를 좀 빡시게 그려야 한다. 셀도 좀 색칠하고...

After we determine which and which methods should be connected with a directed
edge, we then define a conditional probability table for each directed edge.

>>>>

% TODO 아 이거 실제로 돌려봐서 확인해야 할 거 같은데.. 실제로 이렇게 나오나...?

@@

By combining all three kinds of edges, we get a finished graph where every node
is represents a node, and every edge represent how one method relates to another.

@@

After we determine which and which methods should be connected with a directed
edge, we then define a conditional probability table (CPT) for each directed
edge. This step is essential since CPTs are essential components of Bayesian
Networks and we want our big graph to be broken down into small
Bayesian networks. Each node should have its own CPT, and it express how the
node's marginal distribution depends
on those of the parent nodes. We use largely two different CPT schemas:
that of the dataflow-edges and those of the call- and similarity-edges.
Regardless of the schemas, the CPT's size is $4\times 4^n$, where $n$ is the
number of parent nodes of a node. The below figure demonstrates a CPT of a node
with two parent nodes, each shooting a data-flow edge to this node.

% TODO 텍스트로만 써 놓은 걸 실제로 색칠하기.
% VH -> Red, High -> Orange,
% Low -> Green, VL -> Blue
\begin{center}
  \begin{tabular} { |c|c|c|c|c|c|c|c|c|c|c|c|c|c|c|c| }
    \hline
    low  & vl   & vl   & vl   & low  & vl   & vl   & vl   & low  & vl   & vl   & vl   & low  & vl   & vl   & vl  \\
    high & low  & high & high & vl   & low  & vl   & vl   & high & low  & cell & high & high & low  & high & high\\
    high & vl   & low  & high & vl   & vl   & low  & vl   & vl   & vl   & low  & vl   & high & vl   & low  & high\\
    high & vl   & high & vh   & vl   & vl   & vl   & low  & high & vl   & high & vh   & high & vl   & high & vh  \\
    \hline
\end{tabular}
\end{center}

In the above table, red cells should contain very high probabilities, orange
cells should contain relatively high probabilities, whereas green cells should
be assigned low probabilities, and blue cells should be of very low probability.
The idea is this: by the definitions of ``source'', ``sanitizer'', and ``sink'',
data must flow from a source to a sink through possibly a sanitizer, but it
cannot flow in any other sequence of such methods. For example, data cannot
possibly flow from a sink through a source to a sanitizer. Therefore, we encode
this sequence into a tabular form containing probabilities like the above.
